Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-09 presentation/msre-transients.tex
presentation edits

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Description of MSRE Pump Experiments}
  \begin{itemize}
    \item Starting from zero-power critical states with/without forced flow, the fuel salt pump
  was coasted down/started up
    \item Reactor was kept critical by a flux-servo controller moving the rod in response to flux
      changes
  \end{itemize}
  \begin{block}{\textbf{MSR Phenomena Involved}}
    \begin{itemize}
      \item DNP drift under time-varying flow
      \item Loss of delayed neutrons due to out-of-core DNP decay
    \end{itemize}
  \end{block}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/msre-startup}
      \caption{MSRE start-up pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.95\columnwidth]{images/msre-coastdown}
      \caption{MSRE coast-down pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{columns}
    \column{6.5cm}
    \begin{block}{\textbf{Aim of the Study}}
      \begin{itemize}
         \item Develop a V\&V study based on the MSRE pump transients
         \item Verify Moltres against QuasiMolto in collaboration with Aaron Reynolds
           (formerly at Oregon State University)
         \item Validate Moltres against MSRE experimental data for modeling \gls{DNP} drift
       \end{itemize}
    \end{block}
    \begin{block}{\textbf{Modeling Approach}}
      \begin{itemize}
        \item Two neutron energy groups and six DNP groups
        \item Ignored upper and lower plena in the geometry
        \item Looped salt flow with a salt circulation time of 25.2 s
        \item $k$-eigenvalue calculation at every time-step ($dt=0.1$ s) in place of reactivity control
      \end{itemize}
    \end{block}
    \column{4.5cm}
    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.8\columnwidth]{images/msre-2d}
      \caption{2-D axisymmetric model of the \gls{MSRE}.The gray and white regions represent fuel salt
      and graphite, respectively. Fuel salt channels are 1.25-cm wide and spaced at 5-cm intervals.}
      \label{fig:pump-geom}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{$k_\text{eff}$ Under Static \& Steady-Flow Conditions}
  \begin{table}[htb]
    \centering
    \caption{Multiplication factors $k_\text{eff}$ under static and steady salt flow conditions, and
    reactivity changes $\Delta\rho$ due to \gls{DNP} flow from the Moltres and QuasiMolto \gls{MSRE}
    models.}
    \begin{tabular}{l S S S}
      \toprule
      \multirow{2}{*}{Code} & \multicolumn{2}{c}{$k_\text{eff}$} & {$\Delta\rho$ due to} \\
                            & {Static} & {Steady flow} & {\gls{DNP} flow} \\
                            \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-4}
      Moltres & 1.05625 & 1.05311 & -282.4 \\
      QuasiMolto & 1.05603 & 1.05290 & -281.7 \\
      \bottomrule
    \end{tabular}
    \label{table:msre-pump-keff}
  \end{table}
  \begin{itemize}
    \item Excellent agreement between Moltres and QuasiMolto under static and steady-flow conditions prior
  to the pump transients.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Neutron Flux Distributions Under Static Conditions}
  \begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_flux}
      \caption{Normalized centerline neutron fluxes.}
      \label{fig:centerline-flux-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_flux}
      \caption{Normalized midplane neutron fluxes.}
      \label{fig:midplane-flux-dist}
    \end{subfigure}
    \caption{Neutron flux distributions comparing QuasiMolto and Moltres
    \gls{MSRE} models under static conditions. Maximum relative difference $\approx 0.8 \%$.}
    \label{fig:centerline-flux}
  \end{figure}
  \begin{itemize}
    \item Perfect overlap in centerline and midplane neutron fluxes between Moltres and QuasiMolto.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{DNP Distributions Under Static Conditions}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_pre}
      \caption{Normalized centerline \gls{DNP} distributions.}
      \label{fig:centerline-pre-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_pre}
      \caption{Normalized midplane \gls{DNP} distributions.}
      \label{fig:midplane-pre-dist}
    \end{subfigure}
    \caption{\gls{DNP} distribution from Moltres and ratios comparing QuasiMolto and
    Moltres models under static \gls{MSRE} conditions. Maximum relative difference $\approx 0.1 \%$.}
    \label{fig:centerline-pre}
  \end{figure}
  \begin{itemize}
    \item Perfect overlap in centerline and midplane DNP distributions between Moltres and QuasiMolto.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Pump Start-Up Transient Results}
  \begin{columns}
  \column{5.5cm}
  \begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{start-up-v2-reactivity}
    \caption{Reactivity loss (relative to static no-flow conditions) during the \gls{MSRE} pump
    start-up transient.}
    \label{fig:start-up-reactivity}
  \end{figure}
  \column{5.5cm}
  \textbf{Observations}
  \begin{itemize}
    \item Steep initial reactivity loss due to DNP outflow
    \item Reactivity loss plateaus temporarily before dropping due to DNP reentry
    \item Circulation of the excess DNP cause reactivity oscillations
    \item Oscillations eventually dissipate due to decay of excess DNP
    \item Excellent agreement between Moltres and QuasiMolto
  \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Pump Start-Up Transient Results}
  \begin{columns}
  \column{5.5cm}
  \begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{start-up-v2-reactivity}
    \caption{Reactivity loss (relative to static no-flow conditions) during the \gls{MSRE} pump
    start-up transient.}
    \label{fig:start-up-reactivity}
  \end{figure}
  \column{5.5cm}
  \textbf{Discrepancies against MSRE Data}
  \begin{itemize}
    \item MSRE reported a smaller final reactivity loss
    \item MSRE did not report a reactivity plateau (due to DNP present in the upper and lower plena)
    \item MSRE did not log significant reactivity oscillations after the first peak
  \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \textbf{Pump Coast-Down Transient Results}
  \begin{columns}
  \column{5.5cm}
  \begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{coast-down-v2-reactivity}
    \caption{Reactivity loss (relative to static no-flow conditions) during the \gls{MSRE} pump
    coast-down transient.}
    \label{fig:start-up-reactivity}
  \end{figure}
  \column{5.5cm}
  \textbf{Observations}
  \begin{itemize}
    \item Reactivity loss remains briefly stable at the start due to flow inertia
    \item Monotonic decline in reactivity loss over time
  \end{itemize}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{block}{\textbf{Study Outcome}}
    \begin{itemize}
      \item Moltres and QuasiMolto are highly consistent with each other in their looped DNP flow
        modeling capabilities
      \item Moltres and QuasiMolto reproduced key reactivity behavior in response to varying salt
        flow velocities
      \item Some discrepancies observed between the numerical and experimental results due to the
        omission of upper and lower plena
      \item This study can be used for verifying advection capabilities in other MSR simulation tools
      \item The distinct oscillations serve as valuable reference points to facilitate code-to-code
        comparisons
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Description of MSRE Pump Experiments}
  \begin{itemize}
    \item Starting from zero-power critical states under static/steady-flow conditions, the fuel salt pump
  was started up/coasted down.
    \item Reactor was kept critical by a flux-servo controller moving the rod in response to flux
      changes.
  \end{itemize}
  \begin{block}{\textbf{MSR Physics Phenomena Involved}}
    \begin{itemize}
      \item DNP drift under time-varying flow
      \item Loss of delayed neutrons due to out-of-core DNP decay
    \end{itemize}
  \end{block}
  \begin{columns}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/msre-startup}
      \caption{MSRE start-up pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
    \column{5.5cm}
    \begin{figure}
      \centering
      \includegraphics[width=.95\columnwidth]{images/msre-coastdown}
      \caption{MSRE coast-down pump speed and flow rate experimental data
      \cite{prince_zero-power_1968}.}
    \end{figure}
  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{V\&V Study: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{columns}
    \column{6.5cm}
    \begin{block}{\textbf{Aim of the Study}}
      \begin{itemize}
         \item Develop a verification and validation (V\&V) study based on the MSRE pump transients
         \item Verify Moltres against QuasiMolto \cite{reynolds_analysis_2023} in collaboration
           with Dr.\ Aaron Reynolds
         \item Validate Moltres against MSRE experimental data for modeling \gls{DNP} drift
       \end{itemize}
    \end{block}
    \begin{block}{\textbf{Modeling Approach}}
      \begin{itemize}
        \item Two neutron energy groups and six DNP groups
        \item Ignored upper and lower plena in the geometry
%        \item Looped salt flow with a salt circulation time of 25.2 s
        \item $k$-eigenvalue calculation at every time-step ($dt=0.1$ s) in place of reactivity control
      \end{itemize}
    \end{block}
    \column{4.5cm}
    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.8\columnwidth]{images/msre-2d}
      \caption{2-D axisymmetric model of the \gls{MSRE}.The gray and white regions represent fuel salt
      and graphite, respectively. Fuel salt channels are 1.25-cm wide and spaced at 5-cm intervals.}
      \label{fig:pump-geom}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{MSRE $k_\text{eff}$ Estimates Under Static \& Steady-Flow Conditions}
  \begin{table}[htb]
    \centering
    \caption{Multiplication factors $k_\text{eff}$ under static and steady salt flow conditions, and
    reactivity changes $\Delta\rho$ due to \gls{DNP} flow from the Moltres and QuasiMolto \gls{MSRE}
    models.}
    \begin{tabular}{l S S S}
      \toprule
      \multirow{2}{*}{Code} & \multicolumn{2}{c}{$k_\text{eff}$} & {$\Delta\rho$ due to} \\
                            & {Static} & {Steady flow} & {\gls{DNP} flow} \\
                            \cmidrule(r){1-1} \cmidrule(rl){2-3} \cmidrule(l){4-4}
      Moltres & 1.05625 & 1.05311 & -282.4 \\
      QuasiMolto & 1.05603 & 1.05290 & -281.7 \\
      \bottomrule
    \end{tabular}
    \label{table:msre-pump-keff}
  \end{table}
  \begin{itemize}
    \item Excellent agreement between Moltres and QuasiMolto under static and steady-flow conditions prior
  to the pump transients.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Neutron Flux Distributions Under Static Conditions}
  \begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{centerline_flux}
      \caption{Normalized centerline neutron fluxes.}
      \label{fig:centerline-flux-dist}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.48\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{midplane_flux}
      \caption{Normalized midplane neutron fluxes.}
      \label{fig:midplane-flux-dist}
    \end{subfigure}
    \caption{Neutron flux distributions comparing QuasiMolto and Moltres
    \gls{MSRE} models under static conditions. Maximum relative difference $\approx 0.8 \%$.}
    \label{fig:centerline-flux}
  \end{figure}
  \begin{itemize}
    \item Perfect overlap in centerline and midplane neutron fluxes between Moltres and QuasiMolto.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{MSRE Pump Start-Up Transient Results}
  \begin{columns}
  \column{5.5cm}
  \begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{start-up-v2-reactivity}
    \caption{Reactivity loss (relative to static conditions) during the \gls{MSRE} pump
    start-up transient.}
    \label{fig:start-up-reactivity}
  \end{figure}
  \column{5.5cm}
  \textbf{Numerical Results}
  \begin{itemize}
    \item Reactivity loss plateaus after excess DNPs exit.
    \item Circulation of the excess DNPs cause reactivity oscillations that eventually dissipate.
    \item Excellent agreement between Moltres and QuasiMolto.
  \end{itemize}
  \pause
  \textbf{Discrepancies against MSRE Data}
  \begin{itemize}
    \item MSRE had a smaller final reactivity loss.
    \item MSRE did not report a reactivity plateau (due to DNPs present in the upper and lower plena).
    \item MSRE did not log significant reactivity oscillations after the first peak.
  \end{itemize}
  \end{columns}
\end{frame}

%\begin{frame}
%  \frametitle{V\&V Study 2: MSRE Pump Start-up \& Coast-Down Transients}
%  \textbf{Pump Start-Up Transient Results}
%  \begin{columns}
%  \column{5.5cm}
%  \begin{figure}[t]
%    \centering
%    \includegraphics[width=\columnwidth]{start-up-v2-reactivity}
%    \caption{Reactivity loss (relative to static no-flow conditions) during the \gls{MSRE} pump
%    start-up transient.}
%    \label{fig:start-up-reactivity}
%  \end{figure}
%  \column{5.5cm}
%  \textbf{Discrepancies against MSRE Data}
%  \begin{itemize}
%    \item MSRE reported a smaller final reactivity loss
%    \item MSRE did not report a reactivity plateau (due to DNP present in the upper and lower plena)
%    \item MSRE did not log significant reactivity oscillations after the first peak
%  \end{itemize}
%  \end{columns}
%\end{frame}

\begin{frame}
  \frametitle{Pump Coast-Down Transient Results}
  \begin{figure}[t]
    \centering
    \includegraphics[width=.7\columnwidth]{coast-down-v2-reactivity}
    \caption{Reactivity loss (relative to static no-flow conditions) during the \gls{MSRE} pump
    coast-down transient.}
    \label{fig:start-up-reactivity}
  \end{figure}
  Good agreement between numerical and experimental data other than the magnitude differences.
\end{frame}

\begin{frame}
  \frametitle{Summary: MSRE Pump Start-up \& Coast-Down Transients}
  \begin{block}{\textbf{Study Outcome}}
    \begin{itemize}
      \item Moltres and QuasiMolto are highly consistent with each other in their looped DNP flow
        modeling capabilities
      \item Moltres and QuasiMolto reproduced key reactivity behavior in response to varying salt
        flow velocities
      \item Some discrepancies observed between the numerical and experimental results due to the
        omission of upper and lower plena
      \item This study can be used for verifying advection capabilities in other MSR simulation tools
      \item The distinct oscillations serve as valuable reference points to facilitate code-to-code
        comparisons
    \end{itemize}
  \end{block}
\end{frame}

### 2024-12-09 presentation/objectives.tex
slide edits
presentation edits

\begin{frame}
  \frametitle{Objectives}
  \begin{block}{\textbf{Overarching Goal of this Work}}
    \textbf{Improve Moltres as a MSR simulation tool by enabling a wider range of MSR simulation
    scenarios.}
  \end{block}
  \begin{block}{\textbf{Objectives}}
    \begin{enumerate}
      \item \textbf{Improve Multiphysics Capabilities in Moltres}
      \begin{itemize}
        \item \textbf{Verify and Validate Existing Multiphysics Coupling Capabilities in Moltres}
        \item \textbf{Implement a RANS-based Turbulence Model in Moltres}
      \end{itemize}
      \item \textbf{Develop a Hybrid Neutronics Method for Control Rod Modeling in Moltres}
    \end{enumerate}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Objectives}
  \begin{block}{\textbf{Overarching Goal of this Work}}
    Improve Moltres as a MSR simulation tool by enabling a wider range of MSR simulation
    scenarios.
  \end{block}
  \begin{block}{\textbf{Objectives}}
    \begin{enumerate}
      \item \textbf{Improve Multiphysics Capabilities in Moltres}
      \begin{itemize}
        \item Verify and validate existing multiphysics coupling capabilities in Moltres
        \item Implement a RANS-based turbulence model in Moltres
      \end{itemize}
      \item \textbf{Develop a Hybrid Neutronics Method for Control Rod Modeling in Moltres}
      \begin{itemize}
        \item Develop and implement the hybrid $S_N$-diffusion method in Moltres
        \item Verify the hybrid method against high-fidelity neutronics codes and MSRE
          experimental data
        \item Demonstrate a time-dependent reactivity-initiated simulation using the hybrid
          method
      \end{itemize}
    \end{enumerate}
  \end{block}
\end{frame}

### 2024-12-09 presentation/review.tex
presentation edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{Transport-Correction Techniques For Neutron Diffusion-Based Solvers}
  \vspace{.3cm}

  Techniques for augmenting the neutron diffusion method (or equivalent low-order equations) with
  corrections derived from neutron transport:
  \begin{itemize}
    \item Ronen method \cite{ronen_accurate_2004, tomatis_ronen_2021, gross_comprehensive_2023}
    \item Multilevel quasi-diffusion method \cite{goldin_quasi-diffusion_1964, anistratov_computational_2012, tamang_multilevel_2014}
    \item Multischeme transport method \cite{wang_hybrid_2017}
    \item Hybrid transport-diffusion method \cite{anistratov_computational_2012, stehle_hybrid_2014}
  \end{itemize}
  These techniques generally require:
  \begin{itemize}
    \item High-order neutron transport solver
    \item Corrective terms for the neutron diffusion equations
    \item Boundary coupling scheme (for spatial domain decomposition)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{The Ronen Method \cite{ronen_accurate_2004, tomatis_ronen_2021, gross_comprehensive_2023}}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{Multilevel Quasi-Diffusion Method}
  \vspace{.2cm}

  Gol'din originally developed the quasi-diffusion (QD) method as a transport method acceleration
  scheme \cite{goldin_quasi-diffusion_1964}.
  \begin{gather}
    \mbox{\small Zeroth angular moment: } 
    \nabla\cdot J(\vec{r}) + \Sigma_t(\vec{r})\phi(\vec{r}) = \Sigma_{s,0}(\vec{r})\phi(\vec{r}) +
    Q_0(\vec{r}) \label{eq:qd-low-0th} \\
    \mbox{\small First angular moment: }
    \nabla\cdot\left(\vec{\vec{E}}(\vec{r})\phi(\vec{r})\right) + \Sigma_t(\vec{r})J(\vec{r}) =
    \Sigma_{s,1}(\vec{r})J(\vec{r}) + Q_1(\vec{r}) \label{eq:qd-low-1st}
    \shortintertext{\small where}
    \vec{\vec{E}} = \frac{\int_{4\pi}d\hat{\Omega}\ \hat{\Omega}\hat{\Omega}\psi(\vec{r})}{
    \int_{4\pi}d\hat{\Omega}\ \psi(\vec{r})} = \mbox{\small Eddington tensor}.
  \end{gather}
  %
  Gol'din later extended it to a three-level method by deriving effective gray (one-group)
  low-order QD equations \cite{anistratov_solution_1986}.
  \begin{figure}[t]
    \tikzstyle{every node}=[font=\small]
    \centering
    \begin{tikzpicture}
      \node (1) [solver2] {Multigroup high-order transport};
      \node (2) [solver2, right of=1, xshift=3cm] {Multigroup low-order QD};
      \node (3) [solver2, right of=2, xshift=3cm] {Effective low-order transport};
      \draw [arrow] (1.10) -- node[anchor=south, text width=2cm, align=center] {Group\\ Eddington
        and boundary factors} (2.170);
      \draw [arrow] (2.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (1.350);
      \draw [arrow] (2.10) -- node[anchor=south, text width=2cm, align=center] {Collapsed Eddington
        and boundary factors} (3.170);
      \draw [arrow] (3.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (2.350);
    \end{tikzpicture}
    \caption{Algorithm flowchart for the three-level quasi-diffusion method.}
    \label{fig:algorithm}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{Multilevel Quasi-Diffusion Method}
  \vspace{.2cm}

  Tamang \& Anistratov applied the QD method to 1-D time-dependent multiphysics neutron transport
  and heat transfer problems by iteratively coupling the gray low-order equations to the heat
  transfer and precursor equations \cite{tamang_multilevel_2014}.
  \vspace{.2cm}

  Reynolds \& Palmer applied the same approach for steady-state simulations of a 2-D axisymmetric,
  two-group MSRE model \cite{reynolds_analysis_2023}.
  %
  \begin{figure}[h]
    \centering
    \includegraphics[width=.6\columnwidth]{images/reynolds-flux}
    \caption{Fast and thermal fluxes of the 2-D axisymmetric MSRE model by Reynolds \& Palmer
    \cite{reynolds_analysis_2023}.}
    \label{fig:reynolds-flux}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{Multischeme Transport Method}
  \vspace{.2cm}

  Implemented in the Griffin reactor physics application. This method involves making predetermined
  domain decompositions to be treated with the $S_N$, $P_N$, or diffusion methods. Adjoining
  subdomains are coupled through the Lagrange multiplier interface condition:
  \begin{gather}
    -\int_S \left[\left(\llbracket\Psi\rrbracket,\Lambda^*\right)_{\Gamma} +
    \left(\llbracket\Psi^*\rrbracket,\Lambda\right)_{\Gamma}\right] d\hat{\Omega}
    \shortintertext{where}
    \begin{align}
      \llbracket\Psi\rrbracket &= \Psi^+ - \Psi^-, 
      \Psi^\pm = \lim_{s\rightarrow 0^+} \Psi(\vec{x}+s\hat{n}), \nonumber \\
      \Lambda &= \mbox{ Lagrange multiplier},
      \Gamma = \mbox{ interface boundary}, \nonumber \\
      \hat{n} &= \mbox{ normal vector at interface boundary}, \nonumber
    \end{align}
  \end{gather}
  or the upwinding method:
  \begin{gather}
    \int_S \left(|\hat{\Omega}\cdot\hat{n}|\llbracket\Psi^*\rrbracket,\Psi^-\right)_{\Gamma^+}
    d\hat{\Omega} -
    \int_S\left(|\hat{\Omega}\cdot\hat{n}|\llbracket\Psi^*\rrbracket,\Psi^+\right)_{\Gamma^-}
    d\hat{\Omega}
  \end{gather}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Literature Review}
  \textbf{Hybrid Transport-Diffusion Method}
  \vspace{.2cm}

  Anistratov \& Stehle developed an adaptive domain decomposition scheme using Eddington tensor
  estimates as a metric for deducing whether a region is diffusive or
  transport-like \cite{anistratov_computational_2012, stehle_hybrid_2014}.
  \vspace{.2cm}

  It uses two-level neutronics method based on the Second-Moment method \cite{lewis_comparison_1976}.
  The low-order second-moment equations on the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.
\end{frame}

>>>>

\begin{frame}
  \frametitle{Transport-Correction Techniques For Neutron Diffusion-Based Solvers}
  Techniques for augmenting the neutron diffusion method (or equivalent low-order equations) with
  corrections derived from neutron transport:
  \begin{itemize}
    \item Ronen method \cite{ronen_accurate_2004, tomatis_ronen_2021, gross_comprehensive_2023}
    \item Multilevel quasi-diffusion method \cite{goldin_quasi-diffusion_1964, tamang_multilevel_2014, reynolds_analysis_2023}
    \item Multischeme transport method \cite{wang_hybrid_2017}
    \item Hybrid transport-diffusion method \cite{anistratov_computational_2012, stehle_hybrid_2014}
  \end{itemize}
  These techniques generally require:
  \begin{itemize}
    \item High-order neutron transport solver
    \item Corrective terms for the neutron diffusion equations
    \item Boundary coupling scheme (for spatial domain decomposition)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{The Ronen Method}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Multilevel Quasi-Diffusion Method}
  Gol'din originally developed the quasi-diffusion (QD) method as a transport method acceleration
  scheme \cite{goldin_quasi-diffusion_1964}.
  \begin{gather}
    \mbox{\small Zeroth angular moment: } 
    \nabla\cdot J(\vec{r}) + \Sigma_t(\vec{r})\phi(\vec{r}) = \Sigma_{s,0}(\vec{r})\phi(\vec{r}) +
    Q_0(\vec{r}) \label{eq:qd-low-0th} \\
    \mbox{\small First angular moment: }
    \nabla\cdot\left(\vec{\vec{E}}(\vec{r})\phi(\vec{r})\right) + \Sigma_t(\vec{r})J(\vec{r}) =
    \Sigma_{s,1}(\vec{r})J(\vec{r}) + Q_1(\vec{r}) \label{eq:qd-low-1st}
    \shortintertext{\small where}
    \vec{\vec{E}} = \frac{\int_{4\pi}d\hat{\Omega}\ \hat{\Omega}\hat{\Omega}\psi(\vec{r})}{
    \int_{4\pi}d\hat{\Omega}\ \psi(\vec{r})} = \mbox{\small Eddington tensor}.
  \end{gather}
  %
  Gol'din later extended it to a three-level method by deriving effective gray (one-group)
  low-order QD equations \cite{anistratov_solution_1986}.
  \begin{figure}[t]
    \tikzstyle{every node}=[font=\small]
    \centering
    \begin{tikzpicture}
      \node (1) [solver2] {Multigroup high-order transport};
      \node (2) [solver2, right of=1, xshift=3cm] {Multigroup low-order QD};
      \node (3) [solver2, right of=2, xshift=3cm] {Effective low-order transport};
      \draw [arrow] (1.10) -- node[anchor=south, text width=2cm, align=center] {Group\\ Eddington
        and boundary factors} (2.170);
      \draw [arrow] (2.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (1.350);
      \draw [arrow] (2.10) -- node[anchor=south, text width=2cm, align=center] {Collapsed Eddington
        and boundary factors} (3.170);
      \draw [arrow] (3.190) -- node[anchor=north, text width=2cm, align=center] {Effective flux
        and precursors} (2.350);
    \end{tikzpicture}
    \caption{Algorithm flowchart for the three-level quasi-diffusion method.}
    \label{fig:algorithm}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Multilevel Quasi-Diffusion Method}
  Tamang \& Anistratov applied the QD method to 1-D time-dependent multiphysics neutron transport
  and heat transfer problems by iteratively coupling the one-group low-order equations to the heat
  transfer and precursor equations \cite{tamang_multilevel_2014}.
  \vspace{.2cm}

  Reynolds \& Palmer applied the same approach for steady-state simulations of a 2-D axisymmetric,
  two-group MSRE model \cite{reynolds_analysis_2023}.
  %
  \begin{figure}[h]
    \centering
    \includegraphics[width=.6\columnwidth]{images/reynolds-flux}
    \caption{Fast and thermal fluxes of the 2-D axisymmetric MSRE model by Reynolds \& Palmer
    \cite{reynolds_analysis_2023}.}
    \label{fig:reynolds-flux}
  \end{figure}
  \textbf{Limitation: Computational expensive for 3-D full-core simulations.}
\end{frame}

\begin{frame}
  \frametitle{Multischeme Transport Method}
  Implemented in the Griffin reactor physics application \cite{wang_hybrid_2017}. This method
  involves making predetermined
  domain decompositions to be treated with the $S_N$, $P_N$, or diffusion methods. Adjoining
  subdomains are coupled through the Lagrange multiplier interface condition:
  \begin{gather}
    -\int_S \left[\left(\llbracket\Psi\rrbracket,\Lambda^*\right)_{\Gamma} +
    \left(\llbracket\Psi^*\rrbracket,\Lambda\right)_{\Gamma}\right] d\hat{\Omega}
    \shortintertext{where}
    \begin{align}
      \llbracket\Psi\rrbracket &= \Psi^+ - \Psi^-, 
      \Psi^\pm = \lim_{s\rightarrow 0^+} \Psi(\vec{x}+s\hat{n}), \nonumber \\
      \Lambda &= \mbox{ Lagrange multiplier},
      \Gamma = \mbox{ interface boundary}, \nonumber \\
      \hat{n} &= \mbox{ normal vector at interface boundary}, \nonumber
    \end{align}
  \end{gather}
  or the upwinding method:
  \begin{gather}
    \int_S \left(|\hat{\Omega}\cdot\hat{n}|\llbracket\Psi^*\rrbracket,\Psi^-\right)_{\Gamma^+}
    d\hat{\Omega} -
    \int_S\left(|\hat{\Omega}\cdot\hat{n}|\llbracket\Psi^*\rrbracket,\Psi^+\right)_{\Gamma^-}
    d\hat{\Omega}
  \end{gather}
\end{frame}

\begin{frame}
  \frametitle{Hybrid Transport-Diffusion Method \cite{anistratov_computational_2012, stehle_hybrid_2014}}
  \vspace{.2cm}

  Anistratov \& Stehle developed an adaptive domain decomposition scheme using Eddington tensor
  estimates as a metric for deducing whether a region is diffusive or
  transport-like.
  \vspace{.2cm}

  It uses two-level neutronics method based on the Second-Moment method \cite{lewis_comparison_1976}.
  The low-order second-moment equations on the $(s+1)$th iteration are:
  \begin{gather}
    \nabla\cdot J^{(s+1)}+\Sigma_a\phi^{(s+1)} = q, \label{eq:2nd-moment-1} \\
    \frac{1}{3}\nabla\cdot\phi^{(s+1)}+\Sigma_t J^{(s+1)} = \nabla\cdot F^{(s+1/2)}
    \label{eq:2nd-moment-2}
    \shortintertext{where}
    F^{(s+1/2)}_{\alpha\beta} = \int_{4\pi}
    \left(\frac{1}{3}\delta_{\alpha\beta}-\Omega_\alpha\Omega_\beta\right)
    \Psi^{(s+1/2)} d\Omega \label{eq:2nd-moment-3}
  \end{gather}
  %
  The transport subdomains require interface conditions in the form of boundary sources from
  neighboring diffusion subdomains.

  \textbf{Limitation: Complicated implementation and management of computational resources.}
\end{frame}
